\thesistitle

### 2019-08-22 sections/results.tex
Fixed a display issue
Okay here come the results

\section{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

\subsection{Clone Token Volume}
Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease. On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g. the amount of data points the data is based on). As the amount of data points decreases, the datapoints gain less statistical significance.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/duplication}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
  \label{fig:duplication}
\end{figure}

>>>>

\section{Refactoring}
%I think the ultimate goal with this thesis is to do experiments with different clone thresholds. Which thresholds give clones that we should refactor? For this, we will measure the maintainability of the refactored source code over different thresholds. These thresholds range from minimum clone size, variability, and gap size.
In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}). Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring. In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

\subsection{Clone Token Volume}
Figure \ref{fig:tokenvolume} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease. We define the clone volume as the combined number of tokens in all clone instances in a refactored clone class. On the secondary axis (blue line) we plot the amount of times a clone class with the specified amount of tokens is refactored (e.g. the amount of data points the data is based on). As the amount of data points decreases, the datapoints gain less statistical significance.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/Tokenvolume}
  \caption{A graph that shows how the token volume affects the maintainability score of the refactored clone}
  \label{fig:tokenvolume}
\end{figure}

The tokens volume of the clone is equal to the decrease of duplicated tokens. Because of that, what we see in Figure~\ref{fig:tokenvolume} could largely be caused by this metric. Because of that, we also plot graphs in which each metric is considered singularly. In Figure~\ref{fig:}
